Footpath Planning for Example-driven Procedural Road Networks

### 2020-02-05 paper/paper.tex
Paper section oops

\section(Introduction)

\subsection(Research Question)

@@

\subsection(Problem Constraints)

@@

\subsection(Evaluation)

@@

\subsection(Background)

@@

\subsection(ESAL, KTH)
The thesis work will be carried out at the Embodied Social Agents Lab (ESAL) at the Department of Computational Science and Technology (CST). The lab has before been working on systems for generating procedural urban environments, and are interested in the possibility of generating more detailed maps than have been done before, using example-based methods to preserve the aesthetic look of a greater metropolitan area. The lab is particularly interested in the generation of footpaths, since most commercial software that import road maps only import arterial and secondary car roads, and do not include pedestrian walkways, cycle paths and such smaller roads.
% TODO: any official description of ESAL that can be used here?

>>>>

\section{Introduction}

\subsection{Research Question}

@@

\subsection{Problem Constraints}

@@

\subsection{Evaluation}

@@

\subsection{Background}

@@

\subsection{ESAL, KTH}
The thesis work will be carried out at the Embodied Social Agents Lab (ESAL) at the Department of Computational Science and Technology (CST). The lab has before been working on systems for generating procedural urban environments, and are interested in the possibility of generating more detailed maps than have been done before, using example-based methods to preserve the aesthetic look of a greater metropolitan area. The lab is particularly interested in the generation of footpaths, since most commercial software that import road maps only import arterial and secondary car roads, and do not include pedestrian walkways, cycle paths and such smaller roads.
% TODO: any official description of ESAL that can be used here?
